Foundations of ecological and evolutionary change

### 2025-08-04 foundations_of_ecoevo.Rmd
Line 193 Make it clear that this statement means if all else are being equal

In this definition, the longevity of the individual matters.
By definition, an individual that survives from $t$ to $t + 1$ has a higher fitness than one that dies, even if both have the same reproductive output.
With this definition of fitness (eqn 3), we substitute,

>>>>

In this definition, the longevity of the individual matters.
All else being equal, an individual that survives from $t$ to $t + 1$ has a higher fitness than one that dies, even if both have the same reproductive output.
With this definition of fitness (eqn 3), we substitute,
